---
title: "strokeTherapy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup pakcage}
##rm(list=ls())
set.seed(10302020)
library(mgcv)
library(lme4)
```

```{r amplitude_data, echo=FALSE}
x<-read.table("mV.txt",header=TRUE,
              sep="\t",na.strings=c("",".","NA","N/A","NaN"),
              strip.white=TRUE,as.is=TRUE)
dim(x)
head(x)
```

```{r percent_change, echo=FALSE}
x2<-read.table("pctChange.txt",header=TRUE,
               sep="\t",na.strings=c("",".","NA","N/A","NaN"),
               strip.white=TRUE,as.is=TRUE)
dim(x2)
head(x2)
```

```{r check_data_size}
table(unlist(x[,-1]==x2[,-1]))
```
```{r combine_data}
x$pct.change<-x2$pct.change
rm(x2)
x$condBySubject<-paste0(x$subject,x$montage,x$paired.pulse,x$lesional)
x$replicate<-factor(x$replicate)
x$time<-factor(x$time,levels=c(1:5), labels=c("baseline","post1","post2","post3","post4"))
x$montage<-factor(x$montage,levels=c(1:3), labels=c("anodal","bihemi","cathodal"))
x$paired.pulse<-factor(x$paired.pulse,levels=c(1,2,3), labels=c("single","inhibitory","excitory"))
x$lesional<-factor(x$lesional,levels=c(1:2), labels=c("lesional","nonlesional"))
x$subjectID<-factor(x$subjectID)
head(x)
```
```{r}
x
```


```{r add_baseline_means}
bl<-x[x$time=="baseline",]
## baseline mean amplitude by condtion:
bl.means<-tapply(bl$amplitude,bl$condBySubject,mean)
summary(bl.means)
length(bl.means)
length(unique(bl$condBySubject))
x<-merge(x,bl.means,by.x="condBySubject",by.y=0,all.x=TRUE)
colnames(x)[colnames(x)=="y"]<-"BLmeanAmp"
head(x)
```


```{r eda_amplitude}
summary(x$amplitude)
hist(x$amplitude,nclass=50)
```

```{r eda_pctchange}
summary(x$pct.change)
hist(x$pct.change,nclass=50)
```
```{r}
table(x$replicate,useNA="always")
table(x$time,useNA="always")
table(x$montage,useNA="always")
table(x$paired.pulse,useNA="always")
table(x$lesional,useNA="always")
table(x$subjectID,useNA="always")
```

## Linear Mixed Models
```{r lmm}
#mV = BLmV + Time*Montage + (Time|SubjectID)
lmm <- lmer(amplitude ~ BLmeanAmp + time*montage + (time|subjectID), data=x)
summary(lmm)

```

## Non-parametric Repeated Measures ANOVA

```{r additional_packages}
library(tidyverse)
library(ggpubr)
library(rstatix)
```

```{r filter for nonpara}
x_post1 <- x %>%
  filter(time %in% c("baseline","post1"), lesional == "lesional", paired.pulse == "single")
x_post1$amplitude <- scale(x_post1$amplitude)
x_post1 <- x_post1[complete.cases(x_post1), ]
x_post1$time <- factor(x_post1$time, levels=c("baseline","post1"))
#check if the data set is complete
#table(x_post1$time,x_post1$montage,x_post1$subjectID)
```

```{r run anova}
res.aov <- aov(amplitude ~ time*montage + Error(subjectID), data = x_post1)
get_anova_table(res.aov)
# comparisons for montage variable
x_post1 %>%
  pairwise_t_test(
    amplitude ~ montage, paired = TRUE, 
    p.adjust.method = "bonferroni"
    )
# comparisons for time variable
x_post1 %>%
  pairwise_t_test(
    amplitude ~ time, paired = TRUE, 
    p.adjust.method = "bonferroni"
    )
```
In the pairwise test, montage is shown to be significant.

### Check Assumptions
#### Outliers
```{r outliers}
x %>%
  group_by(time) %>%
  identify_outliers(pct.change)
```
There are quite a few extreme outliers in `pct.change` (e.g. a percent change of 617.4672). Thus, the assumption that there were no extreme outliers is violated.

#### Normality
```{r normality}
x %>%
  group_by(time) %>%
  shapiro_test(pct.change)
```

According to the Shapiro-Wilk’s test, since the observed p-values for all categories in `time` are less than 0.05, we reject the null hypothesis that the data are normally distributed.

```{r normality-qqplot}
ggqqplot(x, "pct.change", facet.by = "time")
```
According to the QQ-plot, in all categories in `time`, the larger points deviate significantly from the reference line. Thus, we conclude that the normality assumption is violated.


```{r rv-anova}
# PerCh = 1 + Montage + (1|SubjectID)
friedman.test(pct.change ~ 1 + montage + 1 | subjectID, data = x)

```

